### 2015-07-02 narrative/data-description.tex
section refienment

@@

The user would like the ability to get a certain amount of Quality of Service 
such that they can then make decisions when the expected bandwidth, 
for example is less than what they desire and will then place in a certain set 
of rules which the system can make autonomic decisions to help decide what should be done.
A key insight in this proposed project has been the increased interaction of
the application with the storage system. Towards this end, we propose to
address the quality of service requirements by proivding the application
with mechanisms to specify the quality of I/O service, interrogate the
storage system, and react to the responses. Guided by our past work in
ADIOS \cite{lofstead2008flexible} we propose to explore the design of two
mechanisms for this purpose. Firstly, we will explore the augmentation of
I/O applicatition programing interfaces (I/O APIs) to allow applications to
both specify timing and quality information and also query the storage
system for timing estimates. Through this interface we expect the
application and user to gain insights into how long a single output or input
call will take given the required quality information, and then react to
these estimates by adjusting the quality or restricting the scope of the
data required. Likewise we will explore how an application can provide
timing information to the storage system to allow the storage system to make
optimization decisions to best meet the requirements from the application.

We will also explore external data annotations, such as those
provided by the configuration file in ADIOS. Through the use of these
external augmentation the user can provide insights to the storage system on
the relative value of the data, expected life time and performance
characteristics, as well as relationships between different data sets. With
this information the storage system can make optimizations specific to a use
case. We expect these augmentations to be particularly important for
eviction of data from a storage layer, and migration of data sets to a
different storage layer.

@@

\paragraph{Challenges}
The design of new APIs posses both technical and adoption challenges. Here
we will only consider the technical challenges. The proposed set of APIs aim
to expose broad system level environmental information to the application,
and allow the application to adapt dynamically based on this information.
One aspect of this challenge is the design of an interrogative API that
enables a back-and-forth between the application and the storage system to
enable the application to receive enough information to make adaptation
decisions.

>>>>

%The new APIs will enable the bridge by specifying selectable performance/quality/- cost tradeoffs 
%from both the application and system perspectives based upon the user guided rules/policy and 
%runtime system monitoring status. It allows the middleware to make best possible decisions from 
%the feedback of storage system knowledge, such that it will embed user intentions and the available 
%system storage. 
%We want the system to give the users a certain amount of currency 
%in terms of bandwidth, storage space on each level, and latency expectations. These notions will be fuzzy 
%but they will allow the user to make ad-hoc decisions to figure out what needs to be saved.

@@

In the meanwhile, the user would like the ability to get a certain amount of Quality of Service 
such that they can then make decisions when the expected bandwidth, 
for example is less than what they desire and will then place in a certain set 
of rules which the system can make autonomic decisions to help decide what should be done.
A key insight in this proposed project has been the increased interaction of
the application with the storage system. Towards this end, we propose to
address the quality of service requirements by providing the application
with mechanisms to specify the quality of I/O service, interrogate the
storage system, and react to the responses. Guided by our past work in
ADIOS \cite{lofstead2008flexible} we propose to explore the design of two
mechanisms for this purpose.

Firstly, we will explore the augmentation of
I/O application programing interfaces (I/O APIs) to allow applications to
both specify timing and quality information and also query the storage
system for timing estimates. If user decide to write or read data to or from hierarchical storage systems, 
they will rely on the API to send their intentions for inquiry and examine the system status, 
including how much data they would like to write/read, desired bandwidth, data compression method, etc, 
or the user can express their intension of writing data right now no matter what the traffic is now.
Through this interface we expect the
application and user to gain insights into how long a single output or input
call will take given the required quality information, and then react to
these estimates by adjusting the quality or restricting the scope of the
data required. Likewise we will explore how an application can provide
timing information to the storage system to allow the storage system to make
optimization decisions to best meet the requirements from the application.

Secondly, we will also explore external data annotations, such as those
provided by the configuration file in ADIOS. Through the use of these
external augmentation the user can provide insights to the storage system on
the relative value of the data, expected life time and performance
characteristics, as well as relationships between different data sets. With
this information the storage system can make optimizations specific to a use
case. We expect these augmentations to be particularly important for
eviction of data from a storage layer, and migration of data sets to a
different storage layer.

The capability of APIs provide dynamic runtime information to user and make the system 
more transparent to them rather than a black box. The end user could analyze or visualize data 
in a more comfortable position, where they are able to envision 
how much longer they are going to wait for data.

@@

\paragraph{Challenges:}
The design of new APIs posses both technical and adoption challenges. Here
we will only consider the technical challenges. The proposed set of APIs aim
to expose broad system level environmental information to the application,
and allow the application to adapt dynamically based on this information.
One aspect of this challenge is the design of an interrogative API that
enables a back-and-forth between the application and the storage system to
enable the application to receive enough information to make adaptation
decisions.
